A Critical Review of Sophistication and Model Selection in Algorithmic Statistics

### 2014-12-17 Facticity/Facticity/paper.tex
iets

>>>>

\begin{theorem}[Reduction of Effective Complexity to Structure
  Function]
  There is a constant $c$ such that, for every representation of $x$
  consisting of an ensemble $E$ with $x\in E$ with entropy $H$,
  yielding a total information of $K(E)+H$, there is a finite set $S$
  with $x\in S$ such that $K(S)\le K(E)+c$ and $\log|S|\le H$.
\end{theorem}
\begin{proof}
  First note that although the ensemble $E$ may itself be infinite, it
  is ``typical'', and therefore a valid candidate representation, for
  only a finite number of its elements, namely the set $S=\{y\in E:-\log
  P(y)\le H\} = \{y:P(y)\ge 2^{-H}\}$. Since the sum of probabilities must
  converge, this set cannot be infinite: since $1\ge\sum_{y\in S} P(y)\ge
  \sum_{y\in S}2^{-H} = |S|2^{-H}$ so $|S|\le 2^H$.

\end{proof}
